---
title: "INFO 3010 - Assignment 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## by Lingzi Hong
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Submit this downloaded completed R markdown file in the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 


### Q1: Compute the following values. Write code in the below chunks. (5pts)
(a) Square root of 28 (2pts)
```{r} 
# Create the object x and assign 28 to x then use sqrt function to perform the calculation
x <- 28
sqrt(x)
```

(c) Round to two decimal places for pi, i.e, 3.1415926... (3pts)
```{r}
#Create the object x and assign pi to x1. Then use round function and the digits 
#integer to indicate the number of decimal places which is 2nd in this question
x1 <- pi
round(x1, digits = 2)
```

### Q2: Create the following vectors. a = (5, 10, 15, 20, 70, 120), b = (-7, 6, 18, 3, 58, -56). (10pts) 

(a) create a vector c, which is add results of vector a and b (3pts)
```{r}
#Create a & b vectors and added the total to c. Now I am not sure how to perform the addition for both a & b
# so I just added them manually on vector c. So hopefully that counts or at least from what I got from the 
# instructions
a = c(5, 10, 15, 20, 70, 120)
b = c(-7, 6, 18, 3, 58, -56)
c = c(-2, 16, 33, 23, 128, 64)
```

(b) get the 3rd and 5th element of c  (3pts)
```{r}
#Select the 3rd and 5th element from vector c
c[3]
c[5]
```

(c) how many elements of c are greater than 30 (4pts)
```{r}
#I got the reference from Class2-R Practice on #Who have grade less than 60?
c[c > 30]
```


### Q3: Create the following vectors with seq or rep (10pts)
(a) c(1,2,3,4,1,2,3,4)  (5pts)
```{r}
#I did both seq and req following the steps from
# https://thepracticalr.wordpress.com/2015/03/19/rep-seq-and-cbind-data-creation-and-processing/#:~:text=rep%20and%20seq%20are%20basic,of%20times%20to%20repeat%20it. 
vec1 <- c(1,2,3,4,1,2,3,4)
seq(from = 1, to = 4, by = 1)
rep(1:4, 2)
```

(a) c(1,1,3,3,5,5,7,7)  (5pts)
```{r}
#Same as above assuming that is what this question is asking.
vec2 <- c(1,1,3,3,5,5,7,7)
seq(from = 1, to = 7, by =2)
rep(1:7, 2)
```


### Q4: Create a vector which contains 10 random integer values between -20 and +30. (5pts)
```{r}
#I haven't master this concept yet but if seems like when I execute the vector at the bottom of this comment.
# It will not generarte 10 random numbers within the range but listed all the numbers in between instead.
# However, as I switched to different naming values and it seems like it work.
# Aha, I think I found that you need to use the sample function for this task:
# https://www.statology.org/how-to-generate-a-sample-using-the-sample-function-in-r/
#vec3 <- c(-20:30, size = 10)
#vec3
x3 <- sample(-20:30, 10)
x3
```

### Q5: Get the maximum and minumum value of a vector c(3,-5,8,12,4,2,1,7). (5pts)
```{r}
#Create a vector called numbers and assigned the provided values
#Used max and min function to perform the task
numbers <- c(3,-5,8,12,4,2,1,7)
max(numbers)
min(numbers)
```

### Q6: Write a R program to print the numbers from 1 to 50 and print "Fizz" for multiples of 3, print "Buzz" for multiples of 5, and print "FizzBuzz" for multiples of both. (5pts)
```{r}
#Not sure on how to proceed with this question so I have to Google for reference
#First create the vector with define values from 1 to 50
#But from what I understand, they are using for loop and based off the values from the vector I created above
#Then if n divided by 3 and remains 0 and same with 5 then print FizzBuzz
#Otherwise print Fizz and Buzz respectively. 
n <- c(1:50)
for (n in 1:50)
{
  if (n %% 3 == 0 & n %% 5 == 0) {print("FizzBuzz")}
  else if (n %% 3 == 0) {print("Fizz")}
  else if (n %% 5 == 0) {print("Buzz")}
  else print(n)
}

```

### Q7. Write a R program to get the unique characters of the string "This is a challenging question". (Whitespace can be counted as a unique character) (10pts)
```{r}
#Using Google for this one as well
#Create an object named challenge 
#Use strsplit to split the elements from the object I created earlier. And the last quotation is to specify
# the split argument to be equal to ”“. It is required by default and the quotation determines the amount of 
# space in between
#Use unique() function to eliminate or delete the duplicate values or the rows present in the object
challenge <- "This is a challenging question."
challenge <- strsplit ("This is a challenging question.","")
unique(challenge)

```