---
title: "INFO 3010 - Assignment 2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## by Lingzi Hong
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Fill in the code chunks and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 


### Q1 (5pts): Download the file 'Adults_Cleaned.csv' from canvas. Read the file into a dataframe.
```{r}
setwd('/Users/luhuynh/Desktop/INFO 3010/Week 3')
Adults <- read.csv('Adults_cleaned.csv')
View(Adults)
```


### Q2: (5pts) Check the data type of each column.
```{r}
str(Adults)
```

### Q3: (5pts) How many kinds of occupations are in the dataset?
```{r}
length(unique(Adults$occupation))
```

### Q4: (5pts) Extract 3rd and 5th rows with 1st and 3rd columns from the data frame.
```{r}
Adults[c(3,5), c(1,3)]
```


### Q5: (5pts) How many people work more than 40hrs a week?
```{r}
nrow(Adults[Adults$hours.per.week > 40, ])
```

### Q6: (5pts) Number of people whose native country is Mexico and work more than 40hrs a week.
```{r}
nrow(Adults[Adults$native.country == 'Mexico' & Adults$hours.per.week > 40, ])
```

### Q7: (5pt) For people who have got Bachelors degree, what the is percentage to have capital.gain more than 1000?
```{r}
#Need helps on this one
#Find the number of rows match with the requested conditions
nrow(Adults[Adults$education == 'Bachelors' & Adults$capital.gain > 1000, ]) 

#Find the total rows for this dataset
nrow(Adults)

#Use division to find the percentage
100*(630/2561)
```

### Q8: (5pts) What is the average woking hours per week for people who are husband?
```{r}
mean(Adults[Adults$relationship == "Husband", 'hours.per.week'])
```

### Q9: (5pts) Add a new column to the dataframe, with column name 'health.insurance' and all values as 0. 
```{r}
Adults$health.insurance <- 0

#Check again to see if that added the column with 0 value
View(Adults)
```

### Q10: (5pts) Drop column 'education.num' and 'label' from the data frame. 
```{r}
#Remove columns from positions
Adults[, -c (4 , 15)]

#Check again to see if that it removed the 2 targeted columns
View(Adults)
```